%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{url}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{\LARGE Ari Silburt\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{%{\bf Info} \\ 
Address: 200 Bradley Ave., TV-06, State College, PA 16801 \\ 
Email: ajs725@psu.edu \\
Home Phone: +1 (814) 852-9489 \\ 
Website: \url{https://silburt.github.io/} \\
Linkedin: \url{https://www.linkedin.com/in/ari-silburt/}}

\address{} % Your address 2
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{OBJECTIVE}}

%\vspace{8pt} % Gap between title and text

%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{0.2in} % Some whitespace between sections

\section{\centerline{EDUCATION \& WORK EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl Postdoc, Eberly Fellow, Astrophysics} \hfill 2017--present \\ 
Location: Penn State University, State College, PA, USA \\
Professor: Eric Ford

{\sl Data Scientist, Geotab} \hfill 2017 \\ 
Location: Geotab, Oakville, ON, Canada \\
Manager: Mike Branch \\
Work: Detecting potholes via machine learning from Geotab's vehicle accelerometer data. 

{\sl Doctorate of Philosophy, Astrophysics} \hfill 2012--2017 \\ 
Location: University of Toronto, Toronto, ON, Canada \\
Advisor: Prof. Hanno Rein \\
Thesis: Statistics, Formation and Stability of Exoplanetary Systems. 
 
{\sl Bachelor of Science, Honours Physics} \hfill 2008--2012 \\ 
Location: Mount Allison University, Sackville, NB, Canada \\
Advisor: Prof. David Hornidge \\
Thesis: Improvement of the Compton Beam Asymmetry.
%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	AWARDS & HONORS
%----------------------------------------------------------------------------------------
\section{\centerline{AWARDS \& HONOURS}} 

\vspace{8pt} % Gap between title and text
{\sl Eberly Fellowship}: Awarded to attract exceptional early career scientists to Penn State to \hfill 2017--2019 \\
enhance their career goals in the vibrant, highly collaborative environment.\\ \\
{\sl NSERC PGS-D Research Grant}: Graduate research award from the National Science and \hfill 2015--2017 \\
Engineering Research Council of Canada.\\ \\
{\sl Walter C Sumner Fellowship}: National achievement award for academics and research. \hfill 2015--2017 \\ \\
{\sl SGS Conference Grants}: Two grants from the University of Toronto School of Graduate \hfill 2015, 2016 \\
Studies, awarded for the purpose of presenting original research at top tier conferences. \\ \\
{\sl NSERC CGS-M Research Grant}: Graduate research award from the National Science and \hfill 2013--2014 \\
Engineering Research Council of Canada.\\ \\
{\sl Dr. R. N. Varma Memorial Award}: Graduating Mount Allison University physics student \hfill 2012 \\
with highest GPA. \\ \\
{\sl Donald G. MacGregor Scholarship}: 3rd year Mount Allison University physics student with \hfill 2011 \\ 
highest GPA. \\ \\
{\sl NSERC USRA Research Grant}: Two Undergraduate summer research awards from the  \hfill 2010--2012 \\
National Science and Engineering Research Council of Canada.\\ \\
{\sl Harrison McCain Scholarship}: Mount Allison University scholarship for academic excellence. \hfill 2008--2012 \\

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{\centerline{PUBLICATIONS}} 

\vspace{8pt} % Gap between title and text

{\bf Silburt, A.}, Tamayo, D., Hussain, N., ``{\sl Machine Learning to Predict Orbital Stability: Applications to real planetary systems.}'', 2018, MNRAS (in prep).

Tamayo, D., Hussain, N., {\bf Silburt, A.} ``{\sl Machine Learning to Predict Orbital Stability: Model and API}'', 2018, MNRAS (in prep).

{\bf Silburt, A.}, Ali-Dib, M., et al. ``{\sl Deep Learning on the Moon}'', 2017, EAPSL (in prep).

{\bf Silburt, A.}, Rein, H., ``{\sl Resonant structure, formation and stability of the planetary system HD155358}'', 2017, MNRAS, 469, 4 (6pp)

{\bf Silburt, A.}, Rein, H., Tamayo, D., ``{\sl HERMES: A Hybrid Integrator for Simulating Close Encounters and Planetesimal Migration}'', 2016, \\ preprint: \url{https://silburt.github.io/files/HERMES.pdf}

Tamayo, D., {\bf Silburt, A.}, et al., ``{\sl A Machine Learns to Predict the Stability of Tightly Packed Planetary Systems}'', 2016, ApJL, 832, L22 (5pp)

{\bf Silburt, A.}, Rein, H., ``{\sl Tides Alone Cannot Explain Kepler Planets Close to 2:1 MMR}'', 2015, MNRAS, 453, 4089S (7pp)

{\bf Silburt, A.}, Gaidos, E., Wu, Y., ``{\sl A Statistical Reconstruction of the Planet Population Around Kepler Solar-Type Stars}'', 2015, ApJ,  790, 180S (12pp)

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	TALKS AND POSTERS
%----------------------------------------------------------------------------------------
\section{\centerline{SCIENTIFIC TALKS AND POSTERS}} 

\vspace{8pt} % Gap between title and text
Talk: ``{\sl Machine learning for predicting longterm planetary stability and crater counting on the Moon}", Penn State University Colloquium, 2017. Location: State College, PA, USA. \\ \\
Talk: ``{\sl A Hybrid Integrator for Simulating Planetesimal Migration and Close Encounters}", Numerical Integration Methods in Planetary Sciences, 2017. Location: Toronto, ON, Canada. \\ \\
Talk: ``{\sl The Formation and Stability of Kepler Planets}", Carnegie Institute for Science, 2016. Location: Washington D.C., USA. \\ \\
Talk: ``{\sl Comparing the Formation of Kepler Systems to the Solar System}", Massachusetts Institute of Technology, 2016. Location: Boston, MA, USA. \\ \\
Talk: ``{\sl Machine Learning to Predict Planet Stability}", Stars and Planets Seminar, Harvard University, 2016. Location: Boston, MA, USA. \\ \\
Talk: ``{\sl Forming Planetary Systems: A Comparative Study Between the Solar System and the Kepler Population}", Princeton University's ``Thunch'', 2016. Location: Princeton, NJ, USA. \\ \\
Talk: ``{\sl HERMES: A hybrid integrator for simulating close encounters and planetesimal migration}", Emerging Researchers in Exoplanet Science Symposium II (ERESS II), 2016. Location: Cornell University, NY, USA. \\ \\
Poster: ``{\sl Tidal Forces Cannot Explain Planets Close to 2:1 Mean Motion Resonance}, Extreme Solar Systems III (ESS-III), 2015. Location: Waikoloa Beach, HI, USA. \\ \\
Talk: ``{\sl Sifting Through the Noise: A Re-calculation of the Occurrence of Earth-Sized Planets around Kepler Stars}'', Emerging Researchers in Exoplanet Science Symposium (ERESS), 2015. Location: University Park, PA, USA. \\ \\
Talk: ``{\sl Extracting the Radius Distribution using noisy Kepler Data}", CITA Blackboard Talk, 2015. Location: University of Toronto, Toronto, ON, Canada. \\ \\
Talk: ``{\sl Improving the Beam Asymmetries for Compton Scattering from the 2008 Data}, Atlantic Undergraduate Physics and Astronomy Conference (AUPAC), 2012. Location: Halifax, NS, Canada. \\ \\
Talk: ``{\sl Extracting the Cross Sections and Beam Asymmetries from the 08 Data}, Institut f{\"u}r Kernphysik, 2011. Location: Universit{\"a}t Mainz, Mainz, Germany. \\ \\
Talk: ``{\sl Improving the Beam Asymmetries of the Proton}, Mount Allison Summer Undergraduate Research Fair (SURF), 2011. Location: Sackville, NB, Canada. 

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------
\section{\centerline{TEACHING}} 

\vspace{8pt} % Gap between title and text

I held the position of ``Teaching Assistant" for all entries listed below, and was responsible for leading tutorial lectures, performing planetarium shows, conducting nighttime telescope observing sessions, marking and/or proctoring:

``{\sl PSCB 57: Intro to Scientific Computing"}, University of Toronto. \hfill 2016 \\ \\
``{\sl AST 251: Life on Other Worlds"}, University of Toronto. \hfill 2016 \\ \\
``{\sl AST 210: Great Moments in Astronomy"}, University of Toronto. \hfill 2015 \\ \\
``{\sl AST 101: The Sun and its Neighbours"}, University of Toronto. \hfill 2012--2015 \\ \\
``{\sl AST 201: Stars and Galaxies"}, University of Toronto. \hfill 2013--2014 \\ \\
``{\sl PHYS 1031: Stars, Galaxies and the Universe"}, Mount Allison University. \hfill 2012 \\ \\
``{\sl PHYS 3001: Astrophysics"}, Mount Allison University. \hfill 2011 \\ \\
``{\sl PHYS 3021: Life in the Universe"}, Mount Allison University. \hfill 2011 \\ \\
``{\sl PHYS 1021: Solar System Astronomy"}, Mount Allison University. \hfill 2010 \\ \\
``{\sl PHYS 1551: General Physics II"}, Mount Allison University. \hfill 2010 \\ \\
``{\sl PHYS 1051: General Physics I"}, Mount Allison University. \hfill 2009

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	OUTREACH
%----------------------------------------------------------------------------------------
\section{\centerline{SELECTED LEADERSHIP \& OUTREACH}} 

\vspace{8pt} % Gap between title and text
Executive Secretary, NASA Exoplanet (XRP) review panel. \hfill 2017 \\ \\
``AstroTours" Public Talk: ``{\sl The Butterfly Effect: Chaos Theory and its Influence on our} \hfill 2016 \\ 
{\sl Lives}", University of Toronto, link: \url{https://www.youtube.com/watch?v=kK3Kj1sSUeg} \\ \\
``AstroTours" Keynote Lecture Head Organizer, University of Toronto. Invited Speaker -- \hfill 2016 \\ 
Fran Bagenal, University of Colorado Boulder. \\ \\ 
``AstroTours" Public Talk: ``{\sl A Conversation With Our Old Friend The Moon}",  \hfill 2016 \\ 
University of Toronto, link: \url{https://www.youtube.com/watch?v=HmCa9qN6DVA} \\ \\ 
Scientific Consultant for WJ Gastle's novel ``{\sl Mission 32 (Will Hunter Chronicles Book 1)}". \hfill 2014--2016 \\ \\
Planetarium Operator and Lecturer at the University of Toronto Planetarium. \hfill 2013--2016 \\ \\
Telescope Operator and Volunteer for the University of Toronto's ``AstroTours", \hfill 2012--2016 \\
University of Toronto. \\ \\ 
``AstroTours" Public Talk: ``{\sl Interstellar: The Science Behind the Movie}", University  \hfill 2015 \\ 
of Toronto, link: \url{https://www.youtube.com/watch?v=_mbdxCD_6rA} \\ \\
``AstroTours" Public Talk: ``{\sl Distant Earths}", University of Toronto \hfill 2013 \\
link: \url{https://www.youtube.com/watch?v=mLYzxB8VjQY} \\ \\
Astronomy Society Executive Member, Mount Allison University. \hfill 2010--2012 \\ \\
Telescope Operator for Public Tours and Science Labs, Mount Allison University. \hfill 2009--2012

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


\end{resume} 
\end{document}